Prospects of detecting gamma-ray emission from galaxy clusters: cosmic rays and dark matter annihilations

### 2011-08-02 paper.tex
CR scaling

  \caption{Gamma-ray CR-$\pi^0$ flux within $\rvir$ from brightest 50 clusters in HIFLUGCS catalogue.}
\begin{tabular}{l  c c c c c c c}
 $\eg^2\,\dd F_{\gamma,1.0}/\dd \eg$$^{(5,7)}$\\
 $(5\,\rmn{GeV})$ & $(5\,\rmn{GeV})$ &  $(5\,\rmn{GeV})$\\
PERSEUS  &  68 &  14.28 &  19.15 &  52.49 &  16.26 &  16.25 &  10.06 \\
OPHIUCHU &  96 &   7.71 &  10.34 &  28.33 &   8.78 &   8.78 &   6.01 \\
COMA     &  34 &   4.15 &   5.56 &  15.24 &   4.72 &   4.72 &   2.55 \\
NORMA    &  94 &   2.98 &   3.99 &  10.94 &   3.39 &   3.38 &   2.19 \\
CENTAURU &  30 &   2.61 &   3.50 &   9.58 &   2.97 &   2.97 &   2.62 \\
TRIANGUL &  95 &   1.77 &   2.37 &   6.50 &   2.01 &   2.01 &   0.37 \\
AWM7     &  67 &   1.75 &   2.35 &   6.43 &   1.99 &   1.99 &   1.24 \\
A2319    &  98 &   1.71 &   2.30 &   6.30 &   1.95 &   1.94 &   0.28 \\
A3571    &  39 &   1.61 &   2.15 &   5.90 &   1.83 &   1.82 &   0.41 \\
3C129    &  70 &   1.35 &   1.82 &   4.98 &   1.54 &   1.54 &   0.71 \\
A2199    &  51 &   1.11 &   1.49 &   4.10 &   1.27 &   1.27 &   0.33 \\
2A0335   &  11 &   1.04 &   1.40 &   3.83 &   1.19 &   1.19 &   0.19 \\
A2029    &  43 &   1.04 &   1.39 &   3.81 &   1.18 &   1.17 &   0.08 \\
A0496    &  18 &   1.02 &   1.36 &   3.73 &   1.16 &   1.15 &   0.27 \\
HYDRA    &  25 &   0.95 &   1.27 &   3.48 &   1.08 &   1.08 &   0.84 \\
A0085    &   1 &   0.93 &   1.25 &   3.44 &   1.06 &   1.06 &   0.12 \\
A2142    &  48 &   0.92 &   1.24 &   3.39 &   1.05 &   1.04 &   0.06 \\
A3266    &  17 &   0.92 &   1.23 &   3.37 &   1.05 &   1.04 &   0.16 \\
A1795    &  40 &   0.91 &   1.22 &   3.35 &   1.04 &   1.04 &   0.11 \\
PKS0745  &  77 &   0.82 &   1.10 &   3.02 &   0.94 &   0.88 &   0.03 \\
A2256    &  54 &   0.78 &   1.04 &   2.86 &   0.89 &   0.88 &   0.11 \\
A3558    &  37 &   0.75 &   1.01 &   2.77 &   0.86 &   0.86 &   0.12 \\
A3667    &  56 &   0.71 &   0.96 &   2.62 &   0.81 &   0.80 &   0.07 \\
A1367    &  26 &   0.70 &   0.94 &   2.59 &   0.80 &   0.80 &   0.43 \\
A0478    &  14 &   0.68 &   0.91 &   2.48 &   0.77 &   0.75 &   0.03 \\
A0401    &   8 &   0.61 &   0.82 &   2.25 &   0.70 &   0.68 &   0.05 \\
A0262    &   5 &   0.57 &   0.77 &   2.10 &   0.65 &   0.65 &   0.26 \\
HYDRA-A  &  24 &   0.56 &   0.75 &   2.05 &   0.63 &   0.63 &   0.05 \\
A0754    &  23 &   0.52 &   0.70 &   1.92 &   0.59 &   0.59 &   0.10 \\
A4038    &  62 &   0.52 &   0.69 &   1.90 &   0.59 &   0.59 &   0.13 \\
A2052    &  44 &   0.51 &   0.68 &   1.87 &   0.58 &   0.58 &   0.09 \\
A2147    &  49 &   0.50 &   0.66 &   1.82 &   0.56 &   0.55 &   0.11 \\
A0119    &   2 &   0.48 &   0.64 &   1.76 &   0.54 &   0.54 &   0.10 \\
A0644    &  78 &   0.47 &   0.63 &   1.73 &   0.54 &   0.53 &   0.04 \\
A1644    &  31 &   0.43 &   0.58 &   1.60 &   0.49 &   0.49 &   0.07 \\
A3158    &  13 &   0.39 &   0.53 &   1.45 &   0.45 &   0.44 &   0.04 \\
FORNAX   &  10 &   0.36 &   0.49 &   1.34 &   0.42 &   0.42 &   0.41 \\
A2063    &  47 &   0.36 &   0.48 &   1.33 &   0.41 &   0.41 &   0.06 \\
MKW3S    &  45 &   0.35 &   0.47 &   1.29 &   0.40 &   0.40 &   0.04 \\
A3112    &   9 &   0.34 &   0.46 &   1.26 &   0.39 &   0.38 &   0.02 \\
ZwCl1742 &  97 &   0.34 &   0.46 &   1.25 &   0.39 &   0.38 &   0.03 \\
A4059    &  63 &   0.33 &   0.45 &   1.23 &   0.38 &   0.38 &   0.05 \\
A1651    &  33 &   0.31 &   0.41 &   1.13 &   0.35 &   0.34 &   0.02 \\
A0399    &   7 &   0.31 &   0.41 &   1.13 &   0.35 &   0.34 &   0.02 \\
NGC1550  &  15 &   0.30 &   0.40 &   1.09 &   0.34 &   0.34 &   0.16 \\
ANTLIA   &  79 &   0.29 &   0.39 &   1.06 &   0.33 &   0.33 &   0.22 \\
A2657    &  61 &   0.29 &   0.38 &   1.05 &   0.32 &   0.32 &   0.06 \\
A0539    &  71 &   0.28 &   0.38 &   1.03 &   0.32 &   0.32 &   0.07 \\
A3581    &  41 &   0.28 &   0.37 &   1.03 &   0.32 &   0.32 &   0.07 \\
A2204    &  52 &   0.28 &   0.37 &   1.02 &   0.32 &   0.21 &   0.01 \\
   (2) In units of  $10^{-9} \rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
   (3) In units of  $10^{-10} \rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
   (4) In units of  $10^{-13} \rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
   (5) In units of  $10^{-10} \rmn{erg}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
 \label{tab:flux_tab_CRs}

>>>>

\begin{table*}
\begin{minipage}{2.0\columnwidth}
  \caption{Gamma-ray CR-$\pi^0$ flux within $\rvir$ from brightest 50 clusters in HIFLUGCS catalogue.}
\begin{tabular}{l c c c c c c c}
\hline
\hline
 Cluster & ID$^{(1)}$ & $F_{\gamma}$$^{(2)}$ & $F_{\gamma}$$^{(3)}$&
 $F_{\gamma}$$^{(4)}$ & $\eg^2\,\dd F_{\gamma}/\dd \eg$$^{(5)}$ &
 $\eg^2\,\dd F_{\gamma,0.1}/\dd \eg$$^{(5,6)}$ &
 $\eg^2\,\dd F_{\gamma,1.0}/\dd \eg$$^{(5,7)}$\\
  & & $(>100\,\rmn{MeV})$ & $(>1\,\rmn{GeV})$ & $(>100\,\rmn{GeV})$ &
 $(5\,\rmn{GeV})$ & $(5\,\rmn{GeV})$ & $(5\,\rmn{GeV})$\\
 \hline
PERSEUS & 68 & 14.28 & 19.15 & 52.49 & 16.26 & 16.25 & 10.06 \\
OPHIUCHU & 96 & 7.71 & 10.34 & 28.33 & 8.78 & 8.78 & 6.01 \\
COMA & 34 & 4.15 & 5.56 & 15.24 & 4.72 & 4.72 & 2.55 \\
NORMA & 94 & 2.98 & 3.99 & 10.94 & 3.39 & 3.38 & 2.19 \\
CENTAURU & 30 & 2.61 & 3.50 & 9.58 & 2.97 & 2.97 & 2.62 \\
TRIANGUL & 95 & 1.77 & 2.37 & 6.50 & 2.01 & 2.01 & 0.37 \\
AWM7 & 67 & 1.75 & 2.35 & 6.43 & 1.99 & 1.99 & 1.24 \\
A2319 & 98 & 1.71 & 2.30 & 6.30 & 1.95 & 1.94 & 0.28 \\
A3571 & 39 & 1.61 & 2.15 & 5.90 & 1.83 & 1.82 & 0.41 \\
3C129 & 70 & 1.35 & 1.82 & 4.98 & 1.54 & 1.54 & 0.71 \\
A2199 & 51 & 1.11 & 1.49 & 4.10 & 1.27 & 1.27 & 0.33 \\
2A0335 & 11 & 1.04 & 1.40 & 3.83 & 1.19 & 1.19 & 0.19 \\
A2029 & 43 & 1.04 & 1.39 & 3.81 & 1.18 & 1.17 & 0.08 \\
A0496 & 18 & 1.02 & 1.36 & 3.73 & 1.16 & 1.15 & 0.27 \\
HYDRA & 25 & 0.95 & 1.27 & 3.48 & 1.08 & 1.08 & 0.84 \\
A0085 & 1 & 0.93 & 1.25 & 3.44 & 1.06 & 1.06 & 0.12 \\
A2142 & 48 & 0.92 & 1.24 & 3.39 & 1.05 & 1.04 & 0.06 \\
A3266 & 17 & 0.92 & 1.23 & 3.37 & 1.05 & 1.04 & 0.16 \\
A1795 & 40 & 0.91 & 1.22 & 3.35 & 1.04 & 1.04 & 0.11 \\
PKS0745 & 77 & 0.82 & 1.10 & 3.02 & 0.94 & 0.88 & 0.03 \\
A2256 & 54 & 0.78 & 1.04 & 2.86 & 0.89 & 0.88 & 0.11 \\
A3558 & 37 & 0.75 & 1.01 & 2.77 & 0.86 & 0.86 & 0.12 \\
A3667 & 56 & 0.71 & 0.96 & 2.62 & 0.81 & 0.80 & 0.07 \\
A1367 & 26 & 0.70 & 0.94 & 2.59 & 0.80 & 0.80 & 0.43 \\
A0478 & 14 & 0.68 & 0.91 & 2.48 & 0.77 & 0.75 & 0.03 \\
A0401 & 8 & 0.61 & 0.82 & 2.25 & 0.70 & 0.68 & 0.05 \\
A0262 & 5 & 0.57 & 0.77 & 2.10 & 0.65 & 0.65 & 0.26 \\
HYDRA-A & 24 & 0.56 & 0.75 & 2.05 & 0.63 & 0.63 & 0.05 \\
A0754 & 23 & 0.52 & 0.70 & 1.92 & 0.59 & 0.59 & 0.10 \\
A4038 & 62 & 0.52 & 0.69 & 1.90 & 0.59 & 0.59 & 0.13 \\
A2052 & 44 & 0.51 & 0.68 & 1.87 & 0.58 & 0.58 & 0.09 \\
A2147 & 49 & 0.50 & 0.66 & 1.82 & 0.56 & 0.55 & 0.11 \\
A0119 & 2 & 0.48 & 0.64 & 1.76 & 0.54 & 0.54 & 0.10 \\
A0644 & 78 & 0.47 & 0.63 & 1.73 & 0.54 & 0.53 & 0.04 \\
A1644 & 31 & 0.43 & 0.58 & 1.60 & 0.49 & 0.49 & 0.07 \\
A3158 & 13 & 0.39 & 0.53 & 1.45 & 0.45 & 0.44 & 0.04 \\
FORNAX & 10 & 0.36 & 0.49 & 1.34 & 0.42 & 0.42 & 0.41 \\
A2063 & 47 & 0.36 & 0.48 & 1.33 & 0.41 & 0.41 & 0.06 \\
MKW3S & 45 & 0.35 & 0.47 & 1.29 & 0.40 & 0.40 & 0.04 \\
A3112 & 9 & 0.34 & 0.46 & 1.26 & 0.39 & 0.38 & 0.02 \\
ZwCl1742 & 97 & 0.34 & 0.46 & 1.25 & 0.39 & 0.38 & 0.03 \\
A4059 & 63 & 0.33 & 0.45 & 1.23 & 0.38 & 0.38 & 0.05 \\
A1651 & 33 & 0.31 & 0.41 & 1.13 & 0.35 & 0.34 & 0.02 \\
A0399 & 7 & 0.31 & 0.41 & 1.13 & 0.35 & 0.34 & 0.02 \\
NGC1550 & 15 & 0.30 & 0.40 & 1.09 & 0.34 & 0.34 & 0.16 \\
ANTLIA & 79 & 0.29 & 0.39 & 1.06 & 0.33 & 0.33 & 0.22 \\
A2657 & 61 & 0.29 & 0.38 & 1.05 & 0.32 & 0.32 & 0.06 \\
A0539 & 71 & 0.28 & 0.38 & 1.03 & 0.32 & 0.32 & 0.07 \\
A3581 & 41 & 0.28 & 0.37 & 1.03 & 0.32 & 0.32 & 0.07 \\
A2204 & 52 & 0.28 & 0.37 & 1.02 & 0.32 & 0.21 & 0.01 \\
\hline
\hline
\end{tabular}
\begin{quote}
  Notes:
   (1) The HIFLUGCS cluster ID.
   (2) In units of $10^{-9} \rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
   (3) In units of $10^{-10} \rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
   (4) In units of $10^{-13} \rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
   (5) In units of $10^{-10} \rmn{erg}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
   (6) The flux within $0.1^\circ$, smoothed with a point spread function of $0.1^\circ$.
   (7) The flux within $1.0^\circ$, smoothed with a point spread function of $0.1^\circ$.
 \label{tab:flux_tab_CRs}
  \end{quote}
\end{minipage}
\end{table*}
